---
title: "Data analysis - Imaging data - part 1"
author: "Elsje Burgers"
last modified: "2024-03-25"
output: html_document
---

This script can be used for the first part of the data analysis. It loads the raw data files. Those are filtered and the geometric mean of the GFP data, or the fraction AnV/PI postive cells is computed per image.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r}
rm(list = ls())
library(tidyverse)
```

# Load metadata
These files were created by Wijaya et al. to remove faulty images:  
* out of focus
* compound precipitation
* non-compound specific toxicity (like acidity caused by compound), as seen in lab or in images based on early cell death
```{r}
outputlistpath = "../Data/ImagingData_HepG2/all_data/outputLists"

manual_qc_file_GFP <- read.delim( file = '../Data/ImagingData_HepG2/all_data/metadata/WellExclusionList_GFP.txt', sep = "\t")
manual_qc_file_AnVPI <- read.delim( file = '../Data/ImagingData_HepG2/all_data/metadata/WellExclusionList_AnVPI.txt', sep = "\t")
variable_file <- read.delim( file = '../Data/ImagingData_HepG2/all_data/metadata/variable_names_GFP.txt', sep = "\t")

AnvPI_vars <- c("imageCountParentObj", "PI_masked_primaryID_AreaShape_Area",
                "AnV_masked_primaryID_AreaShape_Area", "Nuclei_AreaShape_Area")

# split up the locationIDs 
manual_qc_file_GFP$locationID <- as.character(manual_qc_file_GFP$locationID)
   tmp_GFP <- lapply(manual_qc_file_GFP$locationID, function(x) {
     strsplit(x, ",") 
   }
   )
names(tmp_GFP) <- manual_qc_file_GFP$plateID

# unlist 1 layer
rm_outliers_GFP <- lapply(tmp_GFP, "[[", 1)

manual_qc_file_AnVPI$locationID <- as.character(manual_qc_file_AnVPI$locationID)
tmp_AnVPI <- lapply(manual_qc_file_AnVPI$locationID, function(x) {
     strsplit(x, ",") 
   }
   )
names(tmp_AnVPI) <- manual_qc_file_AnVPI$plateID

# unlist 1 layer
rm_outliers_AnVPI <- lapply(tmp_AnVPI, "[[", 1)


# check if rm_outliers has correct names
names(rm_outliers_GFP) %in% dir(outputlistpath)
sum(variable_file$plateID %in% dir(outputlistpath))

names(rm_outliers_AnVPI) %in% dir(outputlistpath)
sum(variable_file$plateID %in% dir(outputlistpath))

manual_qc_file_GFP$plateID[manual_qc_file_GFP$plateID %in% variable_file$plateID]
```
# Load data & obtain summarydata
Here, we load the data and apply the desired changes to obtain the summarydata.
```{r}
outputlist_file_paths_GFP <- dir(outputlistpath, 
                        full.names = TRUE, recursive = TRUE, pattern = "GFP")
outputlist_file_paths_AnVPI <- dir(outputlistpath, 
                        full.names = TRUE, recursive = TRUE, pattern = "AnV")


outputlist_file_paths_GFP <- outputlist_file_paths_GFP[!grepl("chunk[1-3]{1}" ,outputlist_file_paths_GFP) ]

outputlist_file_paths_AnVPI <- outputlist_file_paths_AnVPI[!grepl("chunk[1-3]{1}" ,outputlist_file_paths_AnVPI) ]

plateID_str <- unlist(lapply(outputlist_file_paths_GFP, function(paths) {
  gsub("_DA_GFP.Rdata","", gsub("/","", str_extract(string = paths, pattern = "/[A-Za-z0-9-_]{20,40}.Rdata$")))
}
)
)

manual_fileplates <- sort(manual_qc_file_GFP$plateID)
plateID_str <- sort(plateID_str)

data.frame(qc_file = manual_fileplates, plateID_str = plateID_str,
           match = manual_fileplates == plateID_str)
```
```{r}
calc_summaries <- function( paths ) {
  if(!grepl("AnVPI", paths)) {
    isGFP = TRUE
  } else {
    isGFP = FALSE
  }
  
  writeLines(paste(
    "processing: ", paths, "\n GFP data is ", isGFP
  ))
  
load(paths)

if(isGFP) {
  raw_data_GFP <- outputList$myDT

  raw_data_GFP <- raw_data_GFP %>%
    mutate(treatment = gsub("DMEM-noTNF", "DMEM no-TNF", treatment)) %>%
    mutate(cell_line = gsub("HepG2 HMOX-GFP", "HepG2 HMOX1-GFP", cell_line)) %>%
    mutate(cell_line = gsub("HepG2 srxn1-GFP", "HepG2 SRXN1-GFP", cell_line))

  # select data, combine data
  plateID_string <- str_extract(string = paths, pattern = "/[A-Za-z0-9-_]{20,35}.Rdata$")
  plateID_string <- gsub("/","" ,plateID_string)
  plateID_string <- gsub("_DA_GFP.Rdata", "", plateID_string)

  sel_features_GFP <- variable_file %>% filter(plateID == plateID_string)
  if(nrow(sel_features_GFP)== 0) {
    stop("error in plateID from variable_file")
    }
  sel_columns <- unlist(strsplit( x = sel_features_GFP$variable, split = ","))

  sel_data_GFP <- raw_data_GFP %>% 
    select(locationID, treatment, dose_uM, cell_line, plateID, replID, timeID, 
           timeAfterExposure, all_of(sel_columns)) %>% 
    as_tibble()

  # exclude wells based on manual metadata
  eliminate_LocationID_GFP <- manual_qc_file_GFP %>% filter(plateID == plateID_string)
  clean_locationID_GFP <- unlist(strsplit(x = eliminate_LocationID_GFP$locationID, 
                                           split = ","))

  sel_data_GFP <- sel_data_GFP %>% filter(!locationID %in% clean_locationID_GFP)

  # calculate summaries
  var_to_count <- sel_columns[grepl("GFP", sel_columns)]

  # calc summaries
  summary_data <- sel_data_GFP %>% 
    group_by(locationID, treatment, dose_uM, cell_line, plateID, replID, timeID,
             timeAfterExposure) %>%
    summarise(cell_count = mean(imageCountParentObj, na.rm = TRUE),
            GFP_int = exp(mean(log(get(var_to_count)[get(var_to_count)>0]), na.rm= TRUE))
            )

  ##create dose levels
  dose_table <- summary_data %>%
    arrange(plateID, treatment, dose_uM) %>% ungroup %>%
    select(treatment, plateID, dose_uM) %>%
    unique() %>%
    group_by(plateID, treatment) %>%
    mutate(dose_level = 1: n()) %>%
    arrange(plateID, treatment, dose_uM, dose_level)

  summary_data <- left_join(summary_data, dose_table, 
                            by = c("plateID", "treatment", "dose_uM"))

  return(summary_data)


#} else if(!isGFP) {
  # raw_data_AnVPI <- outputList$myDT
  # 
  # sel_data_AnVPI <- raw_data_AnVPI %>% 
  #   select(locationID, treatment, dose_uM, cell_line, plateID, replID, timeID, 
  #          timeAfterExposure, all_of(AnvPI_vars)) %>% 
  #   as_tibble()
  # 
  # 
  # plateID_string_AnVPI <- str_extract(string = paths, pattern = "/[A-Za-z0-9-_]{20,35}.Rdata$")
  # plateID_string_AnVPI <- gsub("/","" ,plateID_string_AnVPI)
  # plateID_string_AnVPI <- gsub("_DA_AnVPI.Rdata", "", plateID_string_AnVPI)
  # 
  # 
  # eliminate_LocationID_AnVPI <- manual_qc_file_AnVPI %>% filter(plateID == plateID_string_AnVPI)
  # clean_locationID_AnVPI <- unlist(strsplit( x = eliminate_LocationID_AnVPI$locationID, split = ","))
  # 
  # sel_data_AnVPI <- sel_data_AnVPI %>% filter(!locationID %in% clean_locationID_AnVPI)
  # 
  # sel_data_AnVPI_complete <- sel_data_AnVPI %>% 
  #   mutate(FractionAnV = AnV_masked_primaryID_AreaShape_Area/Nuclei_AreaShape_Area, 
  #          FractionPI = PI_masked_primaryID_AreaShape_Area/Nuclei_AreaShape_Area)
  # 
  # sel_data_AnVPI_complete[is.na(sel_data_AnVPI_complete)] <- 0
  # 
  # summary_data_AnVPI <- sel_data_AnVPI_complete %>% 
  #   mutate(AnVPos_0 = FractionAnV > 0,
  #          AnVPos_0.1 = FractionAnV > 0.1,
  #          PIPos_0 = FractionPI > 0,
  #          PIPos_0.1 = FractionPI > 0.1) %>%
  #   group_by(locationID,treatment, dose_uM, cell_line, plateID, replID, timeID, 
  #            timeAfterExposure) %>%
  #   summarise(cell_count = mean(imageCountParentObj, na.rm = TRUE),
  #             AnVPos_0 = mean(AnVPos_0),
  #             AnVPos_0.1 = mean(AnVPos_0.1),
  #             PIPos_0 = mean(PIPos_0),
  #             PIPos_0.1 = mean(PIPos_0.1))
  # 
  # ##create dose levels
  # dose_table <- summary_data_AnVPI %>%
  #   arrange(plateID, treatment, dose_uM) %>% ungroup %>%
  #   select(treatment, plateID, dose_uM) %>%
  #   unique() %>%
  #   group_by(plateID, treatment) %>%
  #   mutate(dose_level = 1: n()) %>%
  #   arrange(plateID, treatment, dose_uM, dose_level)
  # 
  # summary_data_AnVPI <- left_join(summary_data_AnVPI, dose_table, 
  #                                 by = c("plateID", "treatment", "dose_uM"))
  # 
  # return(summary_data_AnVPI)
} else {
  stop("not evaluated")
}
  
}

# summary_lists_AnVPI <- lapply(outputlist_file_paths_AnVPI, calc_summaries)
summary_lists_GFP <- lapply(outputlist_file_paths_GFP, calc_summaries)
```

# Save data
```{r}
###GFP###
write_data_fun <- function(f, names) {
  write.table(x = f, file = paste0("../Data/ImagingData_HepG2/all_data/summarydata_GFP/summarydata_GFP_",
                                   names, ".txt"), sep = "\t", row.names = FALSE )
}

mapply(write_data_fun, summary_lists_GFP, plateID_str)

###AnVPI###
# write_data_fun <- function(f, names) {
#   write.table(x = f, file = paste0("../Data/ImagingData_HepG2/all_data/summarydata_AnVPI/summarydata_AnVPI_", 
#                                    names, ".txt"), sep = "\t", row.names = FALSE )
# }

# mapply(write_data_fun, summary_lists_AnVPI, plateID_str)

```
```


