---
title: "Data analysis - Imaging data - part 2"
author: "Elsje Burgers"
last modified: "2025-01-14"
output: html_document
---

This script can be used to obtain the data used for figures and parameter fitting. It uses the output of the script "DataAnalysis_ImagingData_part1".

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
rm(list = ls())
library(tidyverse)

save_data = 0 #if 1 data will be saved as csv, if 0 data will not be saved
```

# Load data
Here, we load the files and correct some minor mistakes in the files to make sure they all use the same way to indicate the cell line etc.
```{r}
data_GFP = do.call(rbind, lapply(list.files(path = "../Data/ImagingData_HepG2/all_data/summarydata_GFP/", 
                                            full.names = TRUE), read.delim))
# data_ANVPI = do.call(rbind, lapply(list.files(path = "../Data/ImagingData_HepG2/all_data/summarydata_AnVPI/", 
#                                               full.names = TRUE), read.delim))

data_GFP$cell_line[data_GFP$cell_line == "HepG2MDM2-GFP"] = "HepG2 MDM2-GFP"
data_GFP$cell_line[data_GFP$cell_line == "HepG2p21-GFP"] = "HepG2 p21-GFP"
data_GFP$cell_line[data_GFP$cell_line == "HepG2 NRF-2-GFP"] = "HepG2 NRF2-GFP"
data_GFP$replID[data_GFP$plateID == "20180329_SBT-TQ_ATF4_rep2"] = 2

# data_ANVPI$cell_line[data_ANVPI$cell_line == "HepG2MDM2-GFP"] = "HepG2 MDM2-GFP"
# data_ANVPI$cell_line[data_ANVPI$cell_line == "HepG2p21-GFP"] = "HepG2 p21-GFP"
# data_ANVPI$cell_line[data_ANVPI$cell_line == "HepG2 NRF-2-GFP"] = "HepG2 NRF2-GFP"
# data_ANVPI$replID[data_ANVPI$plateID == "20180329_SBT-TQ_ATF4_rep2"] = 2

data_GFP = mutate(data_GFP, treatment = gsub(' ', '', treatment))
# data_ANVPI = mutate(data_ANVPI, treatment = gsub(' ', '', treatment))
```

# GFP data
## Mean technical replicates
```{r}
data_GFP_mt = data_GFP %>%
  group_by(treatment, dose_uM, cell_line, plateID, replID, timeID, timeAfterExposure) %>%
  summarise(cell_count = mean(cell_count, na.rm = TRUE),
            GFP_int = mean(GFP_int, na.rm = TRUE))
```

## Correct and normalise
The data is corrected for the background GFP expression by subtracting the intensity for the exposure to 0.01 DMSO from the measured intensity.
There is various ways of normalising the data. In the following chunk it is normalised using the minimal value per plate and the mean value per plate.
```{r}
# Data set containing the 0.01 DMSO values is defined here.
correction = filter(data_GFP_mt, treatment=="DMSO" & dose_uM == 0.01) %>%
  ungroup() %>%
  select(cell_line, plateID, replID, timeID, timeAfterExposure, GFP_int) %>%
  rename(DMSO_value = GFP_int)

# Now the correction is done.
GFP_cor = data_GFP_mt %>%
  left_join(correction) %>%
  mutate(GFP_corrected = ifelse(!is.na(GFP_int),
                          GFP_int - DMSO_value, 
                          GFP_int))

# Here the mean and min value to normalise with are extracted.
plate_mean_min <- GFP_cor %>%
  group_by(cell_line, replID) %>%
  summarise(mean_value = mean(GFP_corrected, na.rm = TRUE),
            min_value = min(GFP_corrected, na.rm = TRUE))

# Min-mean normalization
GFP_normalised <- GFP_cor %>%
  left_join(plate_mean_min) %>%
  mutate(GFP_norm = ifelse(!is.na(GFP_corrected),
                           (GFP_corrected - min_value)/(mean_value - min_value),
                           GFP_corrected))

# Get desired dataset
GFP_realdata = GFP_normalised %>%
  mutate(StateVar = gsub('HepG2 ', '', cell_line )) %>%
  mutate(StateVar = gsub('-GFP', '', StateVar )) %>%
  ungroup() %>%
  select(treatment,dose_uM, replID, timeID, timeAfterExposure, GFP_norm, StateVar) %>%
  rename(data4modelReal = GFP_norm, timeID_orig = timeID) %>%
  mutate(timepoints = round(timeAfterExposure))

# Dataset for steady-states:
GFP_ss = GFP_realdata %>%
  filter(treatment == "DMSO" & dose_uM == 0.01 & timeID_orig == 1) %>%
  group_by(StateVar) %>%
  summarise(steady_state = mean(data4modelReal))

if (0) {#(save_data == 1){
  write.csv(GFP_ss, file = paste("../Data/ImagingData_HepG2/SteadyStates_DMSO_", 
                                  Sys.Date(), ".csv", sep = ""))
}
  
```
## Interpolate
We interpolate the data using a cubic normal spline.
```{r}
tmps = GFP_realdata %>%
  group_by(StateVar, replID) %>%
  summarise(last_tmps = max(timeAfterExposure), first_tmps = min(timeAfterExposure))
max_tmp = min(tmps$last_tmps)

# Now we interpolate the data
interpolation  = GFP_realdata %>%
  group_by(treatment, dose_uM, replID,  StateVar) %>%
  summarise(timepoints = spline(x = timeAfterExposure, y = data4modelReal, 
                                xout = 0:max_tmp, method = "natural")$x, 
            data4modelInterpol = spline(x = timeAfterExposure, y = data4modelReal, 
            xout = 0:max_tmp, method = "natural")$y) %>%
  left_join(GFP_realdata) %>%
  group_by(treatment, dose_uM, replID,  StateVar) %>%
  mutate(data4modelInterpol = ifelse(timepoints < min(timeAfterExposure, na.rm = TRUE)
                                     & is.na(timeAfterExposure),NA, data4modelInterpol))
```
## Filter
We select the compound and doses of interest.
```{r}
compound =  "CDDP" #"DIC" #"NIT"  #"KET"  #
max_dose  = 1000  #404   #120    #66     # 

selected_data = interpolation %>%
    filter(treatment == compound & dose_uM <= max_dose)

print(unique(selected_data$dose_uM))

# selected_data = interpolation %>%
#     filter(treatment == compound & dose_uM == max_dose)
```

## Plot
We plot the data to check if interpolation was done correctly. 
```{r}
# plot all timepoints
plot = ggplot(data = selected_data) + 
  geom_point(aes(x = timepoints, y = data4modelInterpol, color  = as.factor(replID)), shape = 1) + 
  geom_point(aes(x = timeAfterExposure, y = data4modelReal, color  = as.factor(replID)), shape = 2) +
  facet_grid(cols = vars(dose_uM), rows = vars(StateVar), scales = "free")
print(plot)

# plot early timepoints, most errors in extrapolation occur there.
plot = ggplot(data = filter(selected_data, timepoints<10)) + 
  geom_point(aes(x = timepoints, y = data4modelInterpol, color  = as.factor(replID)), shape = 1) + 
  geom_point(aes(x = timeAfterExposure, y = data4modelReal, color  = as.factor(replID)), shape = 3) +
  facet_grid(cols = vars(dose_uM), rows = vars(StateVar), scales = "free")
print(plot)

# for one protein
plot = ggplot(data = filter(selected_data, timepoints<20 & StateVar == "NRF2" )) + 
  geom_point(aes(x = timepoints, y = data4modelInterpol, 
                 shape  = as.factor(replID)), color = "black") +
  geom_point(aes(x = timeAfterExposure, y = data4modelReal, 
                 shape  = as.factor(replID)), color = "red") +
  labs(shape = "replID") + 
  facet_wrap(vars(dose_uM))
print(plot)
```
## Save
If desired, we can save the data here in the format required for the parameter fitting.
```{r}
alldata = selected_data %>%
  mutate(timeID = timepoints+1, dose_uMadj = dose_uM) %>%
  select("StateVar", "replID", "treatment", "timeID", "timeAfterExposure", 
         "dose_uM", "dose_uMadj", "timepoints", "data4modelInterpol", 
         "data4modelReal", "timeID_orig")


fitdata = alldata %>%
  filter(StateVar %in% c("ATF4", "CHOP", "NRF2", "SRXN1"))

if (save_data == 1){
  write.csv(alldata, file = paste("../Data/ImagingData_HepG2/GFPdata_all_", compound, "_", 
                                  Sys.Date(), ".csv", sep = ""))
  write.csv(fitdata, file = paste("../Data/ImagingData_HepG2/GFPdata_4fit_", compound, "_", 
                                  Sys.Date(), ".csv", sep = ""))
}
```

<!-- # Viability data - treatment selection & normalisation -->
<!-- To make it easier to work with, we want to filter the data for the selected treatment and compute the mean of technical replicates, furthermore, we will normalise the cell count. -->
<!-- ## Filter and compute mean of technical replicates -->
<!-- ```{r} -->
<!-- data_ANVPI_filter = data_ANVPI %>% -->
<!--   filter(treatment == compound & timeID<43) %>% -->
<!--   group_by(treatment, dose_uM, cell_line, plateID, replID, timeID, timeAfterExposure) %>% -->
<!--   summarise(cell_count = mean(cell_count, na.rm = TRUE), -->
<!--             AnVPos_0.1 = mean(AnVPos_0.1, na.rm = TRUE), -->
<!--             PIPos_0.1 = mean(PIPos_0.1, na.rm = TRUE)) -->
<!-- ``` -->
<!-- ## Normalise -->
<!-- ```{r} -->
<!-- count0 = data_ANVPI_filter %>% -->
<!--   filter(timeID == 1) %>% -->
<!--   rename(count_t0 = cell_count) %>% -->
<!--   ungroup() %>% -->
<!--   select(treatment, dose_uM, replID, cell_line, count_t0) -->

<!-- data_ANVPI_norm = data_ANVPI_filter %>% -->
<!--   left_join(count0) %>% -->
<!--   mutate(count_norm = cell_count/count_t0) -->
<!-- ``` -->

<!-- # Viability data - compute mean -->
<!-- To compute the mean, the data does not need to be interpolated. We do want to compute the average of all measurements. -->
<!-- ## Average -->
<!-- ```{r} -->
<!-- data_ANVPI_mean = data_ANVPI_norm %>% -->
<!--   group_by(treatment, dose_uM, timeID) %>% -->
<!--   summarise(mean_time = mean(timeAfterExposure, na.rm = TRUE), -->
<!--             mean_count = mean(cell_count, na.rm = TRUE), -->
<!--             sd_count = sd(cell_count, na.rm = TRUE), -->
<!--             mean_count_norm = mean(count_norm, na.rm = TRUE), -->
<!--             sd_count_norm = sd(count_norm, na.rm = TRUE), -->
<!--             mean_PI = mean(PIPos_0.1, na.rm = TRUE), -->
<!--             sd_PI = sd(PIPos_0.1, na.rm = TRUE), -->
<!--             mean_AnV = mean(AnVPos_0.1, na.rm = TRUE), -->
<!--             sd_AnV = sd(AnVPos_0.1, na.rm = TRUE)) -->
<!-- ``` -->

<!-- ## Save -->
<!-- If desired, we can save the data here.  -->
<!-- ```{r} -->
<!-- if (save_data == 1){ -->
<!--   write.csv(data_ANVPI_mean, file = paste("../Data/ImagingData_HepG2/ViabilityData_", compound,  -->
<!--                                           "_", Sys.Date(), ".csv", sep = "")) -->
<!-- } -->
<!-- ``` -->

<!-- # Viability data - adversity model -->
<!-- For fitting the adversity model, we need the relative number of AnV positive cells and of non-AnV positive cells. Moreover, we need to interpolate the data to use it for fitting. -->

<!-- ## Compute relative number of apoptotic and live cells -->
<!-- ```{r} -->
<!-- data_RelativeCount = data_ANVPI_norm %>% -->
<!--   mutate(live_cells = (1-AnVPos_0.1)*count_norm, -->
<!--          apoptotic_cells = (AnVPos_0.1)*count_norm, -->
<!--          total_cells = count_norm, -->
<!--          plate = paste(cell_line, replID), -->
<!--          timepoints = round(timeAfterExposure)) %>% -->
<!--   pivot_longer(c(live_cells, apoptotic_cells, total_cells), names_to = "StateVar",  -->
<!--                values_to = "data4modelReal") %>% -->
<!--   ungroup() %>% -->
<!--   select(treatment, dose_uM, plate, StateVar, data4modelReal, timeAfterExposure,  -->
<!--          timeID, timepoints) -->
<!-- ``` -->

<!-- ##Interpolation -->
<!-- ```{r} -->
<!-- interpolation_AnV  = data_RelativeCount %>% -->
<!--   group_by(treatment, dose_uM, plate, StateVar) %>% -->
<!--   summarise(timepoints = spline(x = timeAfterExposure, y = data4modelReal,  -->
<!--                                 xout = 0:max_tmp, method = "natural")$x,  -->
<!--             data4modelInterpol = spline(x = timeAfterExposure, y = data4modelReal,  -->
<!--             xout = 0:max_tmp, method = "natural")$y) %>% -->
<!--   left_join(data_RelativeCount) %>% -->
<!--   group_by(treatment, dose_uM, plate,  StateVar) %>% -->
<!--   mutate(data4modelInterpol = ifelse(data4modelInterpol<0, 0, data4modelInterpol), -->
<!--          data4modelInterpol = ifelse(timepoints < min(timeAfterExposure, na.rm = TRUE) -->
<!--                                      & is.na(timeAfterExposure),NA, data4modelInterpol)) -->

<!-- # data_RelativeCount = data_RelativeCount %>% -->
<!-- #   mutate(replID3 = match(replID2, unique(data_RelativeCount$replID2))) -->

<!-- ``` -->
<!-- ## Plot -->
<!-- We plot the data to check if interpolation was done correctly.  -->
<!-- ```{r} -->
<!-- # plot all timepoints -->
<!-- for (i in unique(interpolation_AnV$plate)) { -->
<!-- plot = ggplot(data = filter(interpolation_AnV,plate == i)) +  -->
<!--   geom_point(aes(x = timepoints, y = data4modelInterpol,  -->
<!--                  color  = as.factor(dose_uM)), shape = 1) +  -->
<!--   geom_point(aes(x = timeAfterExposure, y = data4modelReal,  -->
<!--                  color  = as.factor(dose_uM)), shape = 2) + -->
<!--   facet_wrap(vars(StateVar), scales = "free") -->
<!-- print(plot) -->
<!-- } -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # # plot early timepoints, most errors in extrapolation occur there. -->
<!-- for (i in unique(interpolation_AnV$plate)) { -->
<!-- plot = ggplot(data = filter(interpolation_AnV,plate == i & timepoints<10)) +  -->
<!--   geom_point(aes(x = timepoints, y = data4modelInterpol,  -->
<!--                  color  = as.factor(dose_uM)), shape = 1) +  -->
<!--   geom_point(aes(x = timeAfterExposure, y = data4modelReal,  -->
<!--                  color  = as.factor(dose_uM)), shape = 2) + -->
<!--   facet_wrap(vars(StateVar), scales = "free") -->
<!-- print(plot) -->
<!-- } -->
<!-- ``` -->
<!-- ## Save -->
<!-- If desired, we can save the data here in the format required for the parameter fitting. -->
<!-- ```{r} -->
<!-- fitdata_AnV = interpolation_AnV %>% -->
<!--   filter(dose_uM <= max_dose) %>% -->
<!--   rename(timeID_orig = timeID) %>% -->
<!--   mutate(timeID = timepoints+1,  -->
<!--          dose_uMadj = dose_uM, -->
<!--          replID = match(plate, unique(interpolation_AnV$plate))) %>% -->
<!--   ungroup() %>% -->
<!--   select("StateVar", "replID", "treatment", "timeID", "timeAfterExposure",  -->
<!--          "dose_uM", "dose_uMadj", "timepoints", "data4modelInterpol",  -->
<!--          "data4modelReal", "timeID_orig") -->

<!-- if (save_data == 1){ -->
<!--   write.csv(fitdata_AnV, file = paste("../Data/ImagingData_HepG2/ANVdata_4fit_", compound, "_", -->
<!--                                   Sys.Date(), ".csv", sep = "")) -->
<!-- } -->
<!-- ``` -->


