---
title: "Figures OSR-ISR stress models"
author: "Elsje Burgers"
last modified: "2025-07-02"
output: html_document
---

This script can be used to simulate the different model versions described in the publication. It can also be used to replicate the figures.

The code to replicate Supplementary Figure S1a, can be found in DataAnalysis_CompoundData.Rmd
The code to replicate Figure 3c and Supplementary Figure S8, can be found in Transcriptomics//Fig3c_S8_TranscriptomicsData.Rmd
The code to replicate Figure 1c  can be found in HepG2_HLCs_PHH_joined_data plot_TD22_TD35_TD37.Rmd
The code to replicate Supplementary Figure 4 can be found in Baseline_Biomarker_Expression.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Some settings

Loading the required packages, functions etc. It is also possible to indicate here if you want to save the images that are being generated.

```{r}
rm(list = ls())
library(tidyverse)
library(deSolve)
library(svglite)

source("functions.R")
source("models.R")

SaveFigures = 0 #if 1 figures will be saved, if 0 figures will not be saved

tspan <-  seq(0, 62, by = 1)

dose_names = as_labeller(c(
  `6`    = "6~mu*M",
  `30`   = "30~mu*M",
  `60`   = "60~mu*M",
  `120`  = "120~mu*M",
  `8`    = "8~mu*M",
  `31`   = "31~mu*M",
  `62`   = "62~mu*M",
  `125`  = "125~mu*M",
  `10`   = "10~mu*M", 
  `50`   = "50~mu*M",
  `101`  = "101~mu*M",
  `202`  = "202~mu*M",
  `404`  = "404~mu*M",
  `6.6`  = "6.6~mu*M",
  `33`   = "33~mu*M",
  `66`   = "66~mu*M",  
  `4`    = "4~mu*M",
  `16`   = "16~mu*M",
  `32`   = "32~mu*M",
  `64`   = "64~mu*M",
  `250`  = "250~mu*M", 
  `500`  = "500~mu*M",
  `0.375`= "0.375~mu*M",
  `0.75` = "0.75~mu*M",
  `1.5`  = "1.5~mu*M",
  `3`    = "3~mu*M",
  `12.5` = "12.5~mu*M",
  `25`   = "25~mu*M",  
  `50`   = "50~mu*M",
  `100`  = "100~mu*M"),
   label_parsed)

```

# Experimental data

First we load the experimental data. The files that are loaded here can be generated with the data analysis scripts if required.

```{r}
# Compound data 
CompoundData_NIT = read.csv(file = "..//Data//CompoundData//CompoundData_Nitrofurantoin_2024-04-17.csv", header=TRUE)
CompoundData_DIC = read.csv(file = "..//Data//CompoundData//CompoundData_Diclofenac_2024-04-17.csv", header=TRUE)
CompoundData_KET = read.csv(file = "..//Data//CompoundData//CompoundData_Ketoconazole_2024-04-17.csv", header=TRUE)
  
# GFP data
GFPData_NIT = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_NIT_2024-03-25.csv", 
                       header=TRUE) %>%
  mutate(dose_uMadj = round(dose_uM, digits = 0),
         replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))
GFPData_DIC = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_DIC_2024-03-25.csv", 
                       header=TRUE) %>%
  mutate(dose_uMadj = round(dose_uM, digits = 0),
         replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))
GFPData_KET = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_KET_2024-03-25.csv", 
                       header=TRUE) %>%
  mutate(dose_uMadj = signif(dose_uM, digits = 2),
         replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))

GFPData_THAP = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_THAP_2025-01-16.csv", 
                       header=TRUE) %>%
  mutate(replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))

GFPData_CDDO = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_CDDO_2025-01-16.csv", 
                       header=TRUE) %>%
  mutate(replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))

GFPData_CDDP = read.csv(file = "..//Data//ImagingData_HepG2//GFPdata_all_CDDP_2025-01-16.csv", 
                       header=TRUE) %>%
  mutate(replID = ifelse(replID == 5, 1, replID),
         StateVar = ifelse(StateVar == "BIP", "BiP", StateVar))

# GSH data
GSHData_NIT = read.csv(file = "..//Data//GSH_LDH_Res//GSHdata_NIT_2024-04-29.csv", header=TRUE)
GSHData_DIC = read.csv(file = "..//Data//GSH_LDH_Res//GSHdata_DIC_2024-05-06.csv", header=TRUE) %>%
  filter(dose_uM<1000)
GSHData_KET = read.csv(file = "..//Data//GSH_LDH_Res//GSHdata_KET_2024-05-06.csv", header=TRUE)

GSSGData = read.csv(file = "..//Data//GSH_LDH_Res//GSH_GSSG_supernatant_intracellular.csv", header = TRUE) %>%
  group_by(treatment, dose_uM, measurement, plate) %>%
  summarise(glutathione = mean(glutathione),
            GSSG = mean(GSSG),
            GSH = mean(GSH))%>%
  ungroup()

# viability data
ViabilityData_NIT = read.csv(file = "..//Data//GSH_LDH_Res//viability_data_NIT.csv", header=TRUE)
ViabilityData_DIC = read.csv(file = "..//Data//GSH_LDH_Res//viability_data_DIC.csv", header=TRUE)
ViabilityData_KET = read.csv(file = "..//Data//GSH_LDH_Res//viability_data_KET.csv", header=TRUE)

ViabilityData = rbind(ViabilityData_NIT, ViabilityData_DIC, ViabilityData_KET)

```

## Compute mean

Here we compute the mean of the experimental data.

```{r}
GFPmean_NIT = GFPData_NIT %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GFPmean_DIC = GFPData_DIC %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GFPmean_KET = GFPData_KET %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GFPmean_THAP = GFPData_THAP %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GFPmean_CDDO = GFPData_CDDO %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GFPmean_CDDP = GFPData_CDDP %>%
  group_by(StateVar, treatment, dose_uMadj, timepoints) %>%
  summarise(mean_interpol = mean(data4modelInterpol, na.rm=TRUE), 
            sd_interpol = sd(data4modelInterpol,na.rm=TRUE)) %>%
  ungroup()

GSHmean_NIT = GSHData_NIT %>%
  group_by(StateVar, treatment, dose_uMadj, timeAfterExposure) %>%
  summarise(mean = mean(data4modelReal, na.rm=TRUE), 
            sd = sd(data4modelReal,na.rm=TRUE)) %>%
  ungroup()

GSHmean_DIC = GSHData_DIC %>%
  group_by(StateVar, treatment, dose_uMadj, timeAfterExposure) %>%
  summarise(mean = mean(data4modelReal, na.rm=TRUE), 
            sd = sd(data4modelReal,na.rm=TRUE)) %>%
  ungroup()

GSHmean_KET = GSHData_KET %>%
  group_by(StateVar, treatment, dose_uMadj, timeAfterExposure) %>%
  summarise(mean = mean(data4modelReal, na.rm=TRUE), 
            sd = sd(data4modelReal,na.rm=TRUE)) %>%
  ungroup()

GSSGMean = GSSGData %>%
  group_by(treatment, dose_uM, measurement) %>%
  summarise(glutathione_mean = mean(glutathione),
            glutathione_sd = sd(glutathione),
            GSSG_mean = mean(GSSG),
            GSSG_sd = sd(GSSG),
            GSH_mean = mean(GSH),
            GSH_sd = sd(GSH)) %>%
  ungroup()
  

```
# Figure 1
## Figure 1a: OSR reporter data NIT

```{r}
reporters_main = c("NRF2", "SRXN1")

Figure1a = ggplot(filter(GFPmean_NIT, StateVar %in% reporters_main)) + theme_classic(base_size = 13) +
  geom_ribbon(aes(x = timepoints, ymin = mean_interpol-sd_interpol,
                  ymax = mean_interpol+sd_interpol,
                  fill = as.factor(dose_uMadj)), alpha = 0.2) +
  geom_ribbon(data = filter(GFPmean_CDDO, StateVar %in% reporters_main & dose_uMadj == 2),
              aes(x = timepoints, ymin = mean_interpol-sd_interpol,
                  ymax = mean_interpol+sd_interpol,linetype = "CDDO"),
                  fill = "orange3", alpha = 0.1) +
  geom_line(data = filter(GFPmean_CDDO, StateVar %in% reporters_main & dose_uMadj == 2),
            aes(x = timepoints, y = mean_interpol, linetype = "CDDO"), 
            color = "orange", linewidth=1) +
  geom_line(aes(x = timepoints, y = mean_interpol, color = as.factor(dose_uMadj)),
            linewidth=1) +
  scale_linetype_discrete(name = "", breaks = "CDDO",
                          labels = expression(paste("2 ", mu, "M CDDO-Me"))) +
  scale_color_viridis_d(aesthetics = c("color", "fill"), breaks = c(6, 30, 60, 120), 
                        labels = c(expression(paste("6 ", mu, "M NIT")),
                                   expression(paste("30 ", mu, "M NIT")),
                                   expression(paste("60 ", mu, "M NIT")),
                                   expression(paste("120 ", mu, "M NIT")))) + 
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + 
  labs(color = "", fill = "") + 
  facet_wrap(vars(StateVar), scales = "free", nrow = 2) + 
  expand_limits(y=0)

print(Figure1a)

if(SaveFigures == 1){
  ggsave("Figure1a.svg", plot = Figure1a, path = "..//Figures", width = 10,
         height = 10, units = "cm", dpi = 300)
}

```

## Figure 1b: UPR reporter data 
```{r}
reporters_main = c("BiP", "XBP1", "CHOP", "ATF4")

Figure1b = ggplot(filter(GFPmean_NIT, StateVar %in% reporters_main)) + theme_classic(base_size = 13) +
  geom_ribbon(aes(x = timepoints, ymin = mean_interpol-sd_interpol,
                  ymax = mean_interpol+sd_interpol, 
                  fill = as.factor(dose_uMadj)), alpha = 0.2) +
  geom_ribbon(data = filter(GFPmean_THAP, StateVar %in% reporters_main & dose_uMadj == 0.05),
              aes(x = timepoints, ymin = mean_interpol-sd_interpol,
                  ymax = mean_interpol+sd_interpol,linetype = "TUN"),
                  fill = "firebrick", alpha = 0.1) +
  geom_line(data = filter(GFPmean_THAP, StateVar %in% reporters_main & dose_uMadj == 0.05),
            aes(x = timepoints, y = mean_interpol, linetype = "TUN"),
            color = "firebrick",linewidth=1) +
  geom_line(aes(x = timepoints, y = mean_interpol, color = as.factor(dose_uMadj)),
            linewidth=1) +
  scale_linetype_discrete(name = "", breaks = "TUN", 
                          labels = expression(paste("0.05 ", mu, "M THAP"))) +
  scale_color_viridis_d(aesthetics = c("color", "fill"), breaks = c(6, 30, 60, 120), 
                        labels = c(expression(paste("6 ", mu, "M NIT")),
                                   expression(paste("30 ", mu, "M NIT")),
                                   expression(paste("60 ", mu, "M NIT")),
                                   expression(paste("120 ", mu, "M NIT")))) + 
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + 
  labs(color = "", fill = "") + 
  facet_wrap(vars(StateVar), scales = "free") + 
  expand_limits(y=0)

print(Figure1b)



if(SaveFigures == 1){
  ggsave("Figure1b.svg", plot = Figure1b, path = "..//Figures", width = 15,
         height = 10, units = "cm", dpi = 300)
}
```

### Supplementary Figure S2: Other reporters NIT
```{r}
reporters_DDR = c("p21", "p53", "MDM2", "BTG2")
FigureS2 = ggplot(filter(GFPmean_NIT, StateVar %in% reporters_DDR)) + 
  theme_classic(base_size = 13) +
  geom_ribbon(aes(x = timepoints, ymin = mean_interpol-sd_interpol,
  ymax = mean_interpol+sd_interpol, fill = as.factor(dose_uMadj)), alpha = 0.2) +
  geom_ribbon(data = filter(GFPmean_CDDP, StateVar %in% reporters_DDR & dose_uMadj == 10),
              aes(x = timepoints, ymin = mean_interpol-sd_interpol,
                  ymax = mean_interpol+sd_interpol, linetype = "CDDP"),
                  fill = "firebrick", alpha = 0.1) +
  geom_line(aes(x = timepoints, y = mean_interpol, color = as.factor(dose_uMadj)),
  linewidth=1) +
    geom_line(data = filter(GFPmean_CDDP, StateVar %in% reporters_DDR & dose_uMadj == 10), 
              aes(x = timepoints, y = mean_interpol, linetype = "CDDP"), colour = "firebrick",
  linewidth=1) +
  scale_linetype_discrete(name = "", breaks = "CDDP", labels = expression(paste("10 ", mu, "M CDDP"))) +
  scale_color_viridis_d(aesthetics = c("color", "fill"), breaks = c(6, 30, 60, 120), 
                        labels = c(expression(paste("6 ", mu, "M NIT")),
                                   expression(paste("30 ", mu, "M NIT")),
                                   expression(paste("60 ", mu, "M NIT")),
                                   expression(paste("120 ", mu, "M NIT")))) + 
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") +
  labs(color = "", fill = "") + 
  facet_wrap(vars(StateVar), scales = "free") + expand_limits(y=2) + expand_limits(y=0)

print(FigureS2)

if(SaveFigures == 1){
  ggsave("FigureS2.pdf", plot = FigureS2, path = "..//Figures", width = 16,
         height = 12, units = "cm", dpi = 300)
}
```

### Supplementary Figure S3: viability data
These figures show the viability data of nitrofurantoin, diclofenac and ketoconazole. This is the LDH increase and resazurin reduction

```{r}
# LDH & resazurin
FigureS3a = ggplot(data = filter(ViabilityData, dose_level > 0 & variable == "Resazurin")) + 
  theme_classic(base_size = 13) +
  geom_ribbon(aes(x = time, ymin = Mean-SD, ymax = Mean+SD,
                  fill = as.factor(dose_level)), alpha = 0.2) +
  geom_line(aes(x = time, y = Mean, color = as.factor(dose_level)),
            linewidth=1) +
  scale_color_viridis_d() + scale_fill_viridis_d() + facet_wrap(~treatment) + 
  scale_y_continuous(breaks = c(0, 25, 50, 75, 100), limits = c(0,110)) +
  xlab("Time (hours)") + ylab("Resazurin reduction [% of control]") +
  labs(color = expression(paste("Concentration  \n level")),
       fill = expression(paste("Concentration  \n level")))

print(FigureS3a)

FigureS3b = ggplot(data = filter(ViabilityData, dose_level > 0 & variable == "LDH")) + 
  theme_classic(base_size = 13) +
  geom_ribbon(aes(x = time, ymin = Mean-SD, ymax = Mean+SD,
                  fill = as.factor(dose_level)), alpha = 0.2) +
  geom_line(aes(x = time, y = Mean, color = as.factor(dose_level)),
            linewidth=1) +
  scale_color_viridis_d() + scale_fill_viridis_d() + facet_wrap(~treatment) +  
  scale_y_continuous(breaks = c(0, 25, 50, 75, 100), limits = c(0,110)) +
  xlab("Time (hours)") + ylab("Extracellular LDH [% of total]") +
  labs(color = expression(paste("Concentration \n level")),
       fill = expression(paste("Concentration \n level")))

print(FigureS3b)

if(SaveFigures == 1){
  ggsave("FigureS3a.svg", plot = FigureS3a, path = "..//Figures", width = 22,
         height = 9, units = "cm", dpi = 300)
  ggsave("FigureS3b.svg", plot = FigureS3b, path = "..//Figures", width = 22,
         height = 9, units = "cm", dpi = 300)
}

```

# Figure 2
## Figure 2a: Compound model simulation for nitrofurantoin
```{r}
CompoundTime = seq(0,48,0.1)
CompoundInistate = c(Compound = 0)
c = 100
sc = 0.0012597

CompoundParms_NIT_M1 = read.csv(file = "..//FittingResults//Compound_M1_20240417_154101_EB_NITModel_parameterEstimates_parmset8_cost_10.60.csv")
  
CompoundECs_NIT = c(CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC1"],
                    CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC2"],
                    CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC3"])

CompoundDoses_NIT = unique(CompoundData_NIT$dose_uM)

CompoundOutput_NIT = run_model(Compound_M1, CompoundTime, CompoundDoses_NIT,
                               CompoundECs_NIT, CompoundInistate,
                               CompoundParms_NIT_M1$X,
                               CompoundParms_NIT_M1$est_value)

Figure2a = ggplot() + theme_classic(base_size = 13) +
  geom_point(data = CompoundData_NIT, 
             aes(x = timeAfterExposure, y = data4modelReal*sc, 
                 color = as.factor(dose_uM)), size = 2, alpha = 0.6) +
  geom_line(data = filter(CompoundOutput_NIT, StateVar == "Compound" & 
                            dose_uMadj == CompoundDoses_NIT[3]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.7) +
  geom_line(data = filter(CompoundOutput_NIT, StateVar == "Compound" & 
                            dose_uMadj == CompoundDoses_NIT[2]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.6) +
  geom_line(data = filter(CompoundOutput_NIT, StateVar == "Compound" & 
                            dose_uMadj == CompoundDoses_NIT[1]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.5) +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) + 
  labs(x = "Time (hours)", y = "Cell-associated nitrofurantoin (nmol/well)", 
       color = expression(paste("Concentration (", mu, "M)"))) +
  scale_y_continuous(trans='log10') +
  expand_limits(y=1)

print(Figure2a)

if(SaveFigures == 1){
  ggsave("Figure2a.svg", plot = Figure2a, path = "..//Figures", width = 14,
         height = 10, units = "cm", dpi = 300)
}
```

## Figure S1b: Nitrofurantoin model and data on linear scale
```{r}
CompoundData_NIT = CompoundData_NIT %>%
    mutate(outlier = ifelse(dose_uM == 7.5 & data4modelReal > 10, TRUE, 
                          ifelse(dose_uM == 30 & data4modelReal > 40, TRUE,
                                 ifelse(dose_uM == 120 & data4modelReal > 100, TRUE, FALSE))))


CompoundData_NIT_stat = CompoundData_NIT %>%
  select(-X) %>% select(-timeID) %>% 
  filter(outlier == FALSE) %>%
  mutate(timeAfterExposure  = paste("t", timeAfterExposure, sep = "")) %>%
  pivot_wider(names_from = timeAfterExposure, values_from = data4modelReal) %>%
  group_by(dose_uM) %>%
  summarise(test24 = t.test(x = t6, y = t24, alternative = c("greater"))$p.value,
            test48 = t.test(x = t6, y = t48, alternative = c("greater"))$p.value)


FigureS1b = ggplot() + theme_classic(base_size = 13) +
  geom_point(data = CompoundData_NIT, 
             aes(x = timeAfterExposure, y = data4modelReal*sc, 
                 color = as.factor(dose_uM)), size = 2, alpha = 0.6) +
  geom_point(data = filter(CompoundData_NIT, outlier == TRUE), 
             aes(x = timeAfterExposure, y = data4modelReal*sc), 
                 color = "red", size = 2, alpha = 0.6) +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) + 
  labs(x = "Time (hours)", y = "Cell-associated nitrofurantoin (nmol/well)", 
       color = expression(paste("Concentration (", mu, "M)"))) +
  facet_wrap(~dose_uM, scales = "free") + expand_limits(y = 0) + 
  theme(legend.position = "bottom")

print(FigureS1b)

if(SaveFigures == 1){
  ggsave("FigureS1b.svg", plot = FigureS1b, path = "..//Figures", width = 21,
         height = 11, units = "cm", dpi = 300)
}


```

## Figure 2c: Stress Pathways model simulations nitrofurantoin
```{r}
reporters_model = c("ATF4", "CHOP", "NRF2", "SRXN1")
GFPData4model_NIT = GFPData_NIT %>% filter(StateVar %in% reporters_model)
GFPmean4model_NIT = GFPmean_NIT %>% filter(StateVar %in% reporters_model)

PathwaysTime = seq(0,62, 0.5)
PathwaysInistate = c(Compound = 0,
                     ATF4 = 0.30702814,
                     CHOP = 0.378908704,
                     KEAP1 = 1,
                     modified_K1 = 0,
                     NRF2 = 0.557889857,
                     SRXN1 = 0.467017171)

PathwaysECs_NIT = c(CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC1"],
                    CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC2"],
                    CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC2"] + (CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC3"] - CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC2"])/3,
                    CompoundParms_NIT_M1$est_value[CompoundParms_NIT_M1$X=="EC3"])

PathwaysDoses_NIT = unique(GFPData_NIT$dose_uMadj)

PathwaysParms_NIT_M2 = read.csv(file = "..//FittingResults//StressPathway_M2_20240626_120618_EB_NITModel_parameterEstimates_parmset35_cost_525.63.csv") %>%
  rbind(CompoundParms_NIT_M1)

PathwaysParms_NIT_M3 = read.csv(file = "..//FittingResults//StressPathway_M3_20240613_090905_EB_NITModel_parameterEstimates_parmset8_cost_374.36.csv") %>%
  rbind(CompoundParms_NIT_M1)

PathwaysOutput_NIT_M2 = run_model(Pathways_M2, PathwaysTime, PathwaysDoses_NIT,
                               PathwaysECs_NIT, PathwaysInistate,
                               PathwaysParms_NIT_M2$X,
                               PathwaysParms_NIT_M2$est_value)
PathwaysOutput_NIT_M3 = run_model(Pathways_M3, PathwaysTime, PathwaysDoses_NIT,
                               PathwaysECs_NIT, PathwaysInistate,
                               PathwaysParms_NIT_M3$X,
                               PathwaysParms_NIT_M3$est_value)

Figure2c = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GFPData4model_NIT, aes(x = timeAfterExposure, 
                                           y = data4modelReal,
                                           shape = as.factor(replID)), col = "grey")+
  geom_line(data = GFPmean4model_NIT, aes(x = timepoints, y = mean_interpol, 
            col = "Mean"), linewidth = 1.5) +
  #simulations
  geom_line(data = filter(PathwaysOutput_NIT_M2, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_NIT_M3, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 2", "Model 3"),
                        values = c("Mean" = "black","Model 2" = "#31688EFF", 
                                   "Model 3" = "#35B779FF"),
                        labels = c("Mean", "\nModel without \nATF4-NRF2 link\n", 
                                   "Model with \nATF4-NRF2 link")) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) + labs(shape = "Replicate")

print(Figure2c)

PathwaysAIC_NIT_M2 = compute_AIC(GFPData4model_NIT, reporters_model, 13, Pathways_M2,
                                 PathwaysDoses_NIT, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_NIT_M2$X, PathwaysParms_NIT_M2$est_value)
PathwaysAIC_NIT_M3 = compute_AIC(GFPData4model_NIT, reporters_model, 14, Pathways_M3,
                                 PathwaysDoses_NIT, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_NIT_M3$X, PathwaysParms_NIT_M3$est_value)

if(SaveFigures == 1){
  ggsave("Figure2c.svg", plot = Figure2c, path = "..//Figures", width = 20,
         height = 15, units = "cm", dpi = 300)
}
```

### Supplemental Figure S5: Full model simulation
```{r}
PathwaysParms_NIT_M1 = read.csv(file = "..//FittingResults//StressPathway_M1_20240531_130410_EB_NITModel_parameterEstimates_parmset58_cost_449.95.csv") %>%
  rbind(CompoundParms_NIT_M1)

PathwaysOutput_NIT_M1 = run_model(Pathways_M1, PathwaysTime, PathwaysDoses_NIT,
                               PathwaysECs_NIT, PathwaysInistate,
                               PathwaysParms_NIT_M1$X,
                               PathwaysParms_NIT_M1$est_value)

FigureS5 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GFPData4model_NIT, aes(x = timeAfterExposure, y = data4modelReal,
                                           shape = as.factor(replID)), col = "gray") +
  geom_line(data = GFPmean4model_NIT, aes(x = timepoints, y = mean_interpol, col = "Mean"),
            linewidth = 1.5) +
  #simulation
  geom_line(data = filter(PathwaysOutput_NIT_M1, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model"),
                        values = c("Mean" = "black","Model" = "#31688EFF")) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) +
  labs(shape = "Replicate")

PathwaysAIC_NIT_M1 = compute_AIC(GFPData4model_NIT, reporters_model, 16, Pathways_M1,
                                 PathwaysDoses_NIT, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_NIT_M1$X, PathwaysParms_NIT_M1$est_value)
print(FigureS5)

if(SaveFigures == 1){
  ggsave("FigureS5.pdf", plot = FigureS5, path = "..//Figures", width = 20,
         height = 15, units = "cm", dpi = 300)
}

```

### Supplemental Figure S6: Model without bound on ATF4-NRF2 model simulation
```{r}
PathwaysParms_NIT_M4 = read.csv(file = "..//FittingResults//StressPathway_M4_20241210_101958_EB_NITModel_parameterEstimates_parmset97_cost_313.07.csv") %>%
  rbind(CompoundParms_NIT_M1)

PathwaysOutput_NIT_M4 = run_model(Pathways_M4, PathwaysTime, PathwaysDoses_NIT,
                               PathwaysECs_NIT, PathwaysInistate,
                               PathwaysParms_NIT_M4$X,
                               PathwaysParms_NIT_M4$est_value)
FigureS6 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GFPData4model_NIT, aes(x = timeAfterExposure, y = data4modelReal,
                                           shape = as.factor(replID)), col = "gray") +
  geom_line(data = GFPmean4model_NIT, aes(x = timepoints, y = mean_interpol, 
                                          col = "Mean"), linewidth = 1.5) +
  #simulation
  geom_line(data = filter(PathwaysOutput_NIT_M4, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model"),
                        values = c("Mean" = "black","Model" = "#31688EFF")) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) +
  labs(shape = "Replicate")

PathwaysAIC_NIT_M4 = compute_AIC(GFPData4model_NIT, reporters_model, 16, Pathways_M4,
                                 PathwaysDoses_NIT, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_NIT_M4$X, PathwaysParms_NIT_M4$est_value)

print(FigureS6)

if(SaveFigures == 1){
  ggsave("FigureS6.pdf", plot = FigureS6, path = "..//Figures", width = 20,
         height = 15, units = "cm", dpi = 300)
}

```

# Figure 3 Glutathione model
## Figure 3b: simulation of glutathione model
```{r}
GSHDoses_NIT = unique(GSHData_NIT$dose_uMadj)

GSHInistate = c(PathwaysInistate, GSH = 1)

GSHParms_NIT_M1 = read.csv(file = "..//FittingResults//GSH_M1_20240613_160637_EB_NITModel_parameterEstimates_parmset24_cost_9.51.csv")
GSHParms_NIT_M1 = GSHParms_NIT_M1 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% GSHParms_NIT_M1$X))
        
GSHParms_NIT_M2 = read.csv(file = "..//FittingResults//GSH_M2_20240621_170031_EB_NITModel_parameterEstimates_parmset27_cost_5.58.csv")
GSHParms_NIT_M2 = GSHParms_NIT_M2 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% GSHParms_NIT_M2$X))


GSHOutput_NIT_M1 = run_model(GSH_M1, PathwaysTime, GSHDoses_NIT,
                               PathwaysECs_NIT, GSHInistate,
                               GSHParms_NIT_M1$X,
                               GSHParms_NIT_M1$est_value) 
GSHOutput_NIT_M2 = run_model(GSH_M2, PathwaysTime, GSHDoses_NIT,
                               PathwaysECs_NIT, GSHInistate,
                               GSHParms_NIT_M2$X,
                               GSHParms_NIT_M2$est_value)

Figure3a = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GSHData_NIT, 
             aes(x = timeAfterExposure, y = data4modelReal, 
                 shape = as.factor(replID)), col = "gray") +
  geom_line(data = GSHmean_NIT, aes(x = timeAfterExposure, y = mean, 
                                    col = "Mean"),linewidth = 1.5) +
  #simulations
  geom_line(data = filter(GSHOutput_NIT_M1, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_NIT_M2, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF"),
                        labels = c("Mean", "\nModel without \nATF4-GSH link\n", "Model with \nATF4-GSH link")) +
  facet_grid(cols = vars(dose_uMadj), labeller = labeller(dose_uMadj = dose_names)) +   
  labs(shape = "Replicate") +
  xlab("Time (hours)") + ylab("Normalised glutathione (-)") + expand_limits(y=0) 

print(Figure3a)

GSHAIC_NIT_M1 = compute_AIC(GSHData_NIT, c("GSH"), 4, GSH_M1, GSHDoses_NIT,
                            PathwaysECs_NIT, GSHInistate, 
                            GSHParms_NIT_M1$X, GSHParms_NIT_M1$est_value)

GSHAIC_NIT_M2 = compute_AIC(GSHData_NIT, c("GSH"), 5, GSH_M2, GSHDoses_NIT,
                            PathwaysECs_NIT, GSHInistate, 
                            GSHParms_NIT_M2$X, GSHParms_NIT_M2$est_value)

if(SaveFigures == 1){
  ggsave("Figure3a.svg", plot = Figure3a, path = "..//Figures", width = 20,
         height = 8, units = "cm", dpi = 300)
}

```
### Supplementary Figure S7: Additional glutathione data
```{r}
FigureS7a = ggplot() + 
  theme_classic(base_size = 11) +
  geom_point(data = filter(GSSGData, measurement == "cells"), 
             aes(x = dose_uM, y = GSH, colour = "GSH"), alpha = 0.7) +
  geom_point(data = filter(GSSGData, measurement == "cells"),
             aes(x = dose_uM, y = GSSG, colour = "GSSG"), alpha = 0.7) +
  geom_line(data = filter(GSSGMean, measurement == "cells"),
            aes(x = dose_uM, y = GSH_mean, colour = "GSH"),  linewidth = 1.5) +
  geom_line(data = filter(GSSGMean, measurement == "cells"),
            aes(x = dose_uM, y = GSSG_mean, colour = "GSSG"),  linewidth = 1.5) +
  facet_grid(cols = vars(treatment), scale = "free") +
  scale_color_viridis_d(name = "", end = 0.4) + 
  # scale_x_continuous(trans='log10') +
  xlab(expression(paste("Concentration (", mu, "M)"))) + ylab(expression(paste("Amount of GSH or GSSG (nmol/mg protein)")))

print(FigureS7a)

FigureS7b = ggplot() + 
  theme_classic(base_size = 11) +
  geom_point(data = GSSGData, aes(x = dose_uM, y = glutathione, colour = measurement), alpha = 0.7) +
  geom_line(data = GSSGMean, aes(x = dose_uM, y = glutathione_mean, colour = measurement),  linewidth = 1.5) +
  facet_grid(cols = vars(treatment), scale = "free") +
  scale_color_viridis_d(name = "", end = 0.4) + 
  # scale_x_continuous(trans='log10') +
  xlab(expression(paste("Concentration (", mu, "M)"))) + ylab(expression(paste("Amount of glutathione (nmol/mg protein)")))

print(FigureS7b)

if(SaveFigures == 1){
  ggsave("FigureS7a.svg", plot = FigureS7a, path = "..//Figures", width = 20,
         height = 8, units = "cm", dpi = 300)
  ggsave("FigureS7b.svg", plot = FigureS7b, path = "..//Figures", width = 20.5,
         height = 8, units = "cm", dpi = 300)
}

```


# Figure 4: Other compounds
### Supplementary Figure S9a: Repoter data diclofenac
```{r}
FigureS9a = ggplot(filter(GFPmean_DIC, StateVar != "HMOX1")) + 
  theme_classic(base_size = 13) +
  geom_ribbon(aes(x = timepoints, ymin = mean_interpol-sd_interpol,
  ymax = mean_interpol+sd_interpol,
  fill = as.factor(dose_uMadj)), alpha = 0.2) +
  geom_line(aes(x = timepoints, y = mean_interpol, color = as.factor(dose_uMadj)),
  linewidth=1) +
   scale_color_viridis_d() + scale_fill_viridis_d() +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") +
  labs(color = expression(paste("Concentration (", mu, "M)")), 
       fill = expression(paste("Concentration (", mu, "M)"))) + 
  facet_wrap(vars(StateVar), scales = "free", nrow = 2) + expand_limits(y=2) + expand_limits(y=0)

print(FigureS9a)

if(SaveFigures == 1){
  ggsave("FigureS9a.svg", plot = FigureS9a, path = "..//Figures", width = 25,
         height = 10, units = "cm", dpi = 300)
}
```
### Supplementary Figure S9b: Repoter data ketoconazole
```{r}
FigureS9b = ggplot(filter(GFPmean_KET, StateVar != "HMOX1")) + 
  theme_classic(base_size = 13) +
  geom_ribbon(aes(x = timepoints, ymin = mean_interpol-sd_interpol,
  ymax = mean_interpol+sd_interpol,
  fill = as.factor(dose_uMadj)), alpha = 0.2) +
  geom_line(aes(x = timepoints, y = mean_interpol, color = as.factor(dose_uMadj)),
  linewidth=1) +
   scale_color_viridis_d() + scale_fill_viridis_d() +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") +
  labs(color = expression(paste("Concentration (", mu, "M)")), 
       fill = expression(paste("Concentration (", mu, "M)"))) + 
  facet_wrap(vars(StateVar), scales = "free", nrow = 2) + 
  expand_limits(y=2) + expand_limits(y=0)

print(FigureS9b)

if(SaveFigures == 1){
  ggsave("FigureS9b.svg", plot = FigureS9b, path = "..//Figures", width = 25,
         height = 10, units = "cm", dpi = 300)
}

```
## Figure 4a: Compound model simulation for diclofenac
```{r}
c = 2500
sc = 0.0009431

CompoundParms_DIC_M1 = read.csv(file = "..//FittingResults//Compound_M1_20240417_154800_EB_DICModel_parameterEstimates_parmset24_cost_172.86.csv")

CompoundECs_DIC = c(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
                    CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"],
                    CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC3"])

CompoundDoses_DIC = unique(CompoundData_DIC$dose_uM)

CompoundOutput_DIC_M1 = run_model(Compound_M1, CompoundTime, CompoundDoses_DIC,
                                  CompoundECs_DIC, CompoundInistate,
                                  CompoundParms_DIC_M1$X,
                                  CompoundParms_DIC_M1$est_value)

Figure4a = ggplot() + theme_classic(base_size = 13) +
  geom_point(data = CompoundData_DIC, 
             aes(x = timeAfterExposure, y = data4modelReal*sc, 
                 color = as.factor(dose_uM)), size = 2, alpha = 0.6) +
  geom_line(data = filter(CompoundOutput_DIC_M1, StateVar == "Compound" & dose_uMadj == CompoundDoses_DIC[3]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.7) +
  geom_line(data = filter(CompoundOutput_DIC_M1, StateVar == "Compound" & dose_uMadj == CompoundDoses_DIC[2]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.6) +
  geom_line(data = filter(CompoundOutput_DIC_M1, StateVar == "Compound"  & dose_uMadj == CompoundDoses_DIC[1]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.5) +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9, 
                        breaks = c(50, 320, 1000)) + 
    labs(x = "Time (hours)", y = "Cell-associated diclofenac (nmol/well)", 
         color = expression(paste("Concentration (", mu, "M)"))) +
  scale_y_continuous(trans='log10') + expand_limits(y=1)
print(Figure4a)

if(SaveFigures == 1){
  ggsave("Figure4a.svg", plot = Figure4a, path = "..//Figures", width = 14,
         height = 10, units = "cm", dpi = 300)
}

```
### Figure 4b & S10: Compound model simulation for ketoconazole
```{r}
c = 2500
sc = 0.00056455
# KET
CompoundParms_KET_M1 = read.csv(file = "..//FittingResults//Compound_M1_20240417_154056_EB_KETModel_parameterEstimates_parmset7_cost_500.94.csv")
CompoundParms_KET_M2 = read.csv(file = "..//FittingResults//Compound_M2_20240417_162403_EB_KETModel_parameterEstimates_parmset21_cost_457.96.csv")

CompoundECs_KET_M1 = c(CompoundParms_KET_M1$est_value[CompoundParms_KET_M1$X=="EC1"],
                       CompoundParms_KET_M1$est_value[CompoundParms_KET_M1$X=="EC2"],
                       CompoundParms_KET_M1$est_value[CompoundParms_KET_M1$X=="EC3"])

CompoundDoses_KET = unique(CompoundData_KET$dose_uM)

CompoundOutput_KET_M1 = run_model(Compound_M1, CompoundTime, CompoundDoses_KET,
                                  CompoundECs_KET_M1, CompoundInistate,
                                  CompoundParms_KET_M1$X,
                                  CompoundParms_KET_M1$est_value)

CompoundECs_KET_M2 = c(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"],
                       CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"],
                       CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"])

CompoundOutput_KET_M2 = run_model(Compound_M2, CompoundTime, CompoundDoses_KET,
                                  CompoundECs_KET_M2, CompoundInistate,
                                  CompoundParms_KET_M2$X,
                                  CompoundParms_KET_M2$est_value)

FigureS10 = ggplot() + theme_classic(base_size = 13) +
  geom_point(data = CompoundData_KET, 
             aes(x = timeAfterExposure, y = data4modelReal*sc, 
                 color = as.factor(dose_uM)), size = 2, alpha = 0.6) +
  geom_line(data = filter(CompoundOutput_KET_M1, StateVar == "Compound" & dose_uMadj == CompoundDoses_KET[3]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.7) +
  geom_line(data = filter(CompoundOutput_KET_M1, StateVar == "Compound" & dose_uMadj == CompoundDoses_KET[2]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.6) +
  geom_line(data = filter(CompoundOutput_KET_M1, StateVar == "Compound"  & dose_uMadj == CompoundDoses_KET[1]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.5) +
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) + 
    labs(x = "Time (hours)", y = "Cell-associated ketoconazole (nmol/well)",  
         color = expression(paste("Concentration (", mu, "M)"))) +
    scale_y_continuous(trans='log10') + expand_limits(y=1)

print(FigureS10)

Figure4b = ggplot() + theme_classic(base_size = 13) +
  geom_point(data = CompoundData_KET, 
             aes(x = timeAfterExposure, y = data4modelReal*sc, 
                 color = as.factor(dose_uM)), size = 2, alpha = 0.6) +
  geom_line(data = filter(CompoundOutput_KET_M2, StateVar == "Compound" & dose_uMadj == CompoundDoses_KET[3]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.7) +
  geom_line(data = filter(CompoundOutput_KET_M2, StateVar == "Compound" & dose_uMadj == CompoundDoses_KET[2]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.6) +
  geom_line(data = filter(CompoundOutput_KET_M2, StateVar == "Compound"  & dose_uMadj == CompoundDoses_KET[1]), 
            aes(x = time, y = c*value*sc, color = as.factor(dose_uMadj)),
            linewidth = 1.5) + 
  scale_color_viridis_d(option = "plasma", begin = 0.1, end = 0.9) + 
    labs(x = "Time (hours)", y = "Cell-associated ketoconazole (nmol/well)", 
         color = expression(paste("Concentration (", mu, "M)"))) +
    scale_y_continuous(trans='log10') + expand_limits(y=1)

print(Figure4b)

if(SaveFigures == 1){
  ggsave("FigureS10.pdf", plot = FigureS10, path = "..//Figures", width = 14,
         height = 10, units = "cm", dpi = 300)
  ggsave("Figure4b.svg", plot = Figure4b, path = "..//Figures", width = 14,
         height = 10, units = "cm", dpi = 300)
}

```


## Figure 4c: Stress pathway model simulation for diclofenac 
```{r}
GFPData4model_DIC = GFPData_DIC %>% filter(StateVar %in% reporters_model)
GFPmean4model_DIC = GFPmean_DIC %>% filter(StateVar %in% reporters_model)


PathwaysECs_DIC = c(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]/5,
        CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
        CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"] + (50/270)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"]-CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]),
        CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"] + (150/270)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"]-CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]),
        CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"] + (80/680)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC3"]-CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"])
)

PathwaysDoses_DIC = unique(GFPData_DIC$dose_uMadj)

# only sc_ISR and sc_OSR 
PathwaysParms_DIC_M1 = read.csv(file = "..//FittingResults//StressPathway_M1_20240613_154822_EB_DICModel_parameterEstimates_parmset43_cost_9283.09.csv") %>%
  rbind(CompoundParms_DIC_M1)
PathwaysParms_DIC_M1 = PathwaysParms_DIC_M1 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% PathwaysParms_DIC_M1$X))

# sc_ISR and sc_OSR, Vmax_C and V_degN2
PathwaysParms_DIC_M2 = read.csv(file = "..//FittingResults//StressPathway_M2_20240613_155106_EB_DICModel_parameterEstimates_parmset18_cost_5573.09.csv") %>%
  rbind(CompoundParms_DIC_M1)
PathwaysParms_DIC_M2 = PathwaysParms_DIC_M2 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% PathwaysParms_DIC_M2$X))

# sc_ISR and sc_OSR, Vmax_C, V_degN2, buildA4 and V_N2A4
PathwaysParms_DIC_M3 = read.csv(file = "..//FittingResults//StressPathway_M3_20240807_111458_EB_DICModel_parameterEstimates_parmset7_cost_2720.80.csv") %>%
  rbind(CompoundParms_DIC_M1)
PathwaysParms_DIC_M3 = PathwaysParms_DIC_M3 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% PathwaysParms_DIC_M3$X))

PathwaysOutput_DIC_M1 = run_model(PathwaysDIC_M1, PathwaysTime, PathwaysDoses_DIC,
                               PathwaysECs_DIC, PathwaysInistate,
                               PathwaysParms_DIC_M1$X,
                               PathwaysParms_DIC_M1$est_value)

PathwaysOutput_DIC_M2 = run_model(PathwaysDIC_M1, PathwaysTime, PathwaysDoses_DIC,
                               PathwaysECs_DIC, PathwaysInistate,
                               PathwaysParms_DIC_M2$X,
                               PathwaysParms_DIC_M2$est_value)

PathwaysOutput_DIC_M3 = run_model(PathwaysDIC_M1, PathwaysTime, PathwaysDoses_DIC,
                               PathwaysECs_DIC, PathwaysInistate,
                               PathwaysParms_DIC_M3$X,
                               PathwaysParms_DIC_M3$est_value)

Figure4c = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = filter(GFPData4model_DIC, dose_uMadj %in% c(101, 404)), 
                           aes(x = timeAfterExposure, y = data4modelReal,
                               shape = as.factor(replID)), col = "grey")+
  geom_line(data = filter(GFPmean4model_DIC, dose_uMadj %in% c(101, 404)), 
            aes(x = timepoints, y = mean_interpol, col = "Mean"), 
            linewidth = 1.5) +
  #simulations
  geom_line(data = filter(PathwaysOutput_DIC_M1, StateVar %in% reporters_model &
                            dose_uMadj %in% c(101, 404)),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_DIC_M2, StateVar %in% reporters_model & 
                            dose_uMadj %in% c(101, 404)),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_DIC_M3, StateVar %in% reporters_model &
                            dose_uMadj %in% c(101, 404)),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                        labels = c("Mean ", "\nModel without \nrecalibration \n", 
                                   "Model with \nrecalibrating \nVmaxC\n", 
                                   "Model with \nrecalibrating \nVmaxC, bA4, \nVdegN2 & VN2")) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) + labs(shape = "Replicate")

print(Figure4c)

PathwaysAIC_DIC_M1 = compute_AIC(GFPData4model_DIC, reporters_model, 2, PathwaysDIC_M1,
                                 PathwaysDoses_DIC, PathwaysECs_DIC, PathwaysInistate,
                                 PathwaysParms_DIC_M1$X, PathwaysParms_DIC_M1$est_value)
PathwaysAIC_DIC_M2 = compute_AIC(GFPData4model_DIC, reporters_model, 4, PathwaysDIC_M1,
                                 PathwaysDoses_DIC, PathwaysECs_DIC, PathwaysInistate,
                                 PathwaysParms_DIC_M2$X, PathwaysParms_DIC_M2$est_value)
PathwaysAIC_DIC_M3 = compute_AIC(GFPData4model_DIC, reporters_model, 4, PathwaysDIC_M1,
                                 PathwaysDoses_DIC, PathwaysECs_DIC, PathwaysInistate,
                                 PathwaysParms_DIC_M3$X, PathwaysParms_DIC_M3$est_value)

if(SaveFigures == 1){
  ggsave("Figure4c.svg", plot = Figure4c, path = "..//Figures", width = 14,
         height = 15, units = "cm", dpi = 300)
}
```

## Supplementary Figure S11: All doses stress pathway model simulation for diclofenac 
```{r}
FigureS11 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GFPData4model_DIC, aes(x = timeAfterExposure, 
                                           y = data4modelReal,
                                           shape = as.factor(replID)), col = "grey")+
  geom_line(data = GFPmean4model_DIC, aes(x = timepoints, y = mean_interpol,
            col = "Mean"), linewidth = 1.5) +
  #simulations
  geom_line(data = filter(PathwaysOutput_DIC_M1, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_DIC_M2, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_DIC_M3, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                        labels = c("Mean ", "\nModel without \nrecalibration \n", 
                                   "Model with \nrecalibrating \nVmaxC\n", 
                                   "Model with \nrecalibrating \nVmaxC, bA4, \nVdegN2 & VN2")) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) + labs(shape = "Replicate")

print(FigureS11)


if(SaveFigures == 1){
  ggsave("FigureS11.pdf", plot = FigureS11, path = "..//Figures", width = 25,
         height = 15, units = "cm", dpi = 300)
}
```

### Figure 4d: Stress pathway model simulation for ketoconazole 
```{r}
GFPData4model_KET = GFPData_KET %>% filter(StateVar %in% reporters_model)
GFPmean4model_KET = GFPmean_KET %>% filter(StateVar %in% reporters_model)

PathwaysECs_KET = c(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] +
                      (6.3/20.7)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"]-
                                  CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
                    CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] +
                      (12/62)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"]-
                                 CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"]),
                    CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] +
                      (45/62)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"]-
                                 CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"])
                    )

PathwaysDoses_KET = unique(GFPData_KET$dose_uMadj)

PathwaysParms_KET_M1 = read.csv(file = "..//FittingResults//StressPathway_M1_20240613_154110_EB_KETModel_parameterEstimates_parmset7_cost_2904.86.csv") %>%
  rbind(CompoundParms_KET_M2)

PathwaysParms_KET_M1 = PathwaysParms_KET_M1 %>%
  rbind(filter(PathwaysParms_NIT_M3, !X %in% PathwaysParms_KET_M1$X))

PathwaysParms_KET_M2 = read.csv(file = "..//FittingResults//StressPathway_M2_20240722_121100_EB_KETModel_parameterEstimates_parmset49_cost_1701.75.csv")

PathwaysParms_KET_M2 = PathwaysParms_KET_M2 %>%
  rbind(filter(PathwaysParms_KET_M1, !X %in% PathwaysParms_KET_M2$X))

PathwaysOutput_KET_M1 = run_model(PathwaysKET_M1, PathwaysTime, PathwaysDoses_KET,
                               PathwaysECs_KET, PathwaysInistate,
                               PathwaysParms_KET_M1$X,
                               PathwaysParms_KET_M1$est_value)

PathwaysOutput_KET_M2 = run_model(PathwaysKET_M1, PathwaysTime, PathwaysDoses_KET,
                               PathwaysECs_KET, PathwaysInistate,
                               PathwaysParms_KET_M2$X,
                               PathwaysParms_KET_M2$est_value)

Figure4d = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = filter(GFPData4model_KET, dose_uMadj %in% c(6.6, 66)), 
                           aes(x = timeAfterExposure, y = data4modelReal,
                               shape = as.factor(replID)), col = "grey")+
  geom_line(data = filter(GFPmean4model_KET, dose_uMadj %in% c(6.6, 66)), 
            aes(x = timepoints, y = mean_interpol, col = "Mean"), 
            linewidth = 1.5) +
  #simulations
  geom_line(data = filter(PathwaysOutput_KET_M1, StateVar %in% reporters_model &
                             dose_uMadj %in% c(6.6, 66)),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_KET_M2, StateVar %in% reporters_model &
                             dose_uMadj %in% c(6.6, 66)),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF"),
                        labels = c("Mean ", "\nModel without \nrecalibration \n", 
                                   "Model with \nrecalibrating \nVmaxC")) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) + labs(shape = "Replicate")

print(Figure4d)

PathwaysAIC_KET_M1 = compute_AIC(GFPData4model_KET, reporters_model, 2, PathwaysKET_M1,
                                 PathwaysDoses_KET, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_KET_M1$X, PathwaysParms_KET_M1$est_value)
PathwaysAIC_KET_M2 = compute_AIC(GFPData4model_KET, reporters_model, 3, PathwaysKET_M1,
                                 PathwaysDoses_KET, PathwaysECs_NIT, PathwaysInistate,
                                 PathwaysParms_KET_M2$X, PathwaysParms_KET_M2$est_value)

if(SaveFigures == 1){
  ggsave("Figure4d.svg", plot = Figure4d, path = "..//Figures", width = 14,
         height = 15, units = "cm", dpi = 300)
}
```

### Supplementary Figure S12: All doses stress pathway model simulation for ketoconazole 
```{r}
FigureS12 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GFPData4model_KET, aes(x = timeAfterExposure, 
                                           y = data4modelReal,
                                           shape = as.factor(replID)), col = "grey")+
  geom_line(data = GFPmean4model_KET, aes(x = timepoints, y = mean_interpol, 
            col = "Mean"), linewidth = 1.5) +
  #simulations
  geom_line(data = filter(PathwaysOutput_KET_M1, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(PathwaysOutput_KET_M2, StateVar %in% reporters_model),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  facet_grid(cols = vars(dose_uMadj), rows = vars(StateVar), scales = "free",
             labeller = labeller(dose_uMadj = dose_names)) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF"),
                        labels = c("Mean", "\nModel without \nrecalibration \n", 
                                   "Model with \nrecalibrating \nVmaxC")) +
  xlab("Time (hours)") + ylab("Normalised GFP intensity (-)") + expand_limits(y=0) + labs(shape = "Replicate")

print(FigureS12)

if(SaveFigures == 1){
  ggsave("FigureS12.pdf", plot = FigureS12, path = "..//Figures", width = 18,
         height = 15, units = "cm", dpi = 300)
}

```

## Figure 4e: Glutathione model simulation for diclofenac
```{r}
GSHDoses_DIC = unique(GSHData_DIC$dose_uMadj)

GSHECs_DIC = c((4/50)*CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
               (8/50)*CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
               (16/50)*CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
               (32/50)*CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"],
               CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"] +
                 (14/270)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"] -
                             CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]),
               CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"] +
                 (75/270)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"] -
                             CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]),
               CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"] +
                 (200/270)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"] -
                              CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC1"]),
               CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"] +
                 (180/680)*(CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC3"] -
                              CompoundParms_DIC_M1$est_value[CompoundParms_DIC_M1$X=="EC2"])
               )

GSHParms_DIC_M1 = PathwaysParms_DIC_M3 %>% 
  rbind(filter(GSHParms_NIT_M2, !X %in% PathwaysParms_DIC_M3$X))

GSHParms_DIC_M2 = 
  read.csv(file = "..//FittingResults//GSH_M2_20240807_154130_EB_DICModel_parameterEstimates_parmset48_cost_44.49.csv")
GSHParms_DIC_M2 = GSHParms_DIC_M2 %>%
  rbind(filter(GSHParms_DIC_M1, !X %in% GSHParms_DIC_M2$X))

GSHParms_DIC_M3 = 
  read.csv(file = "..//FittingResults//GSH_M3_20240807_155325_EB_DICModel_parameterEstimates_parmset1_cost_29.32.csv")
GSHParms_DIC_M3 = GSHParms_DIC_M3 %>%
  rbind(filter(GSHParms_DIC_M1, !X %in% GSHParms_DIC_M3$X))


GSHOutput_DIC_M1 = run_model(GSHDIC_M1, PathwaysTime, GSHDoses_DIC,
                               GSHECs_DIC, GSHInistate,
                               GSHParms_DIC_M1$X,
                               GSHParms_DIC_M1$est_value) 
GSHOutput_DIC_M2 = run_model(GSHDIC_M1, PathwaysTime, GSHDoses_DIC,
                               GSHECs_DIC, GSHInistate,
                               GSHParms_DIC_M2$X,
                               GSHParms_DIC_M2$est_value)
GSHOutput_DIC_M3 = run_model(GSHDIC_M1, PathwaysTime, GSHDoses_DIC,
                               GSHECs_DIC, GSHInistate,
                               GSHParms_DIC_M3$X,
                               GSHParms_DIC_M3$est_value)

Figure4e = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = filter(GSHData_DIC, dose_uMadj %in% c(125, 500)),
             aes(x = timeAfterExposure, y = data4modelReal, 
                 shape = as.factor(replID)), col = "gray", show_guide = FALSE) +
  geom_line(data = filter(GSHmean_DIC, dose_uMadj %in% c(125, 500)), 
            aes(x = timeAfterExposure, y = mean, 
                col = "Mean"),linewidth = 1.5) +
  #simulations
  geom_line(data = filter(GSHOutput_DIC_M1, StateVar == "GSH" & 
                            dose_uMadj %in% c(125, 500)),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_DIC_M2, StateVar == "GSH" &
                            dose_uMadj %in% c(125, 500)),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_DIC_M3, StateVar == "GSH" &
                            dose_uMadj %in% c(125, 500)),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                        values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                   "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                        labels = c("Mean ", "\nModel without \nrecalibration \n", 
                                   "Model with \nrecalibrating \nVmaxG \n",
                                   "Model with \nrecalibrating \nVmaxG & dA4G")) +
  facet_wrap(vars(dose_uMadj), labeller = labeller(dose_uMadj = dose_names)) +
  labs(shape = "Replicate") +
  xlab("Time (hours)") + ylab("Normalised glutathione (-)") + expand_limits(y=0) 

print(Figure4e)

GSHAIC_DIC_M1 = compute_AIC(GSHData_DIC, c("GSH"), 0, GSHDIC_M1, GSHDoses_DIC,
                            GSHECs_DIC, GSHInistate,
                            GSHParms_DIC_M1$X, GSHParms_DIC_M1$est_value)

GSHAIC_DIC_M2 = compute_AIC(GSHData_DIC, c("GSH"), 1, GSHDIC_M1, GSHDoses_DIC,
                            GSHECs_DIC, GSHInistate,
                            GSHParms_DIC_M2$X, GSHParms_DIC_M2$est_value)

GSHAIC_DIC_M3 = compute_AIC(GSHData_DIC, c("GSH"), 2, GSHDIC_M1, GSHDoses_DIC,
                            GSHECs_DIC, GSHInistate,
                            GSHParms_DIC_M3$X, GSHParms_DIC_M3$est_value)

if(SaveFigures == 1){
  ggsave("Figure4e.svg", plot = Figure4e, path = "..//Figures", width = 15,
         height = 6, units = "cm", dpi = 300)
}

```

### Supplementary Figure S13: all doses for glutathione model DIC
```{r}
FigureS13 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GSHData_DIC, 
             aes(x = timeAfterExposure, y = data4modelReal, 
                 shape = as.factor(replID)), col = "gray") +
  geom_line(data = GSHmean_DIC, aes(x = timeAfterExposure, y = mean, 
                                    col = "Mean"),linewidth = 1.5) +
  #simulations
  geom_line(data = filter(GSHOutput_DIC_M1, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_DIC_M2, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
    geom_line(data = filter(GSHOutput_DIC_M3, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                     values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                     labels = c("Mean", "\nModel without \nrecalibration \n",
                                "Model with \nrecalibrating \nVmaxG \n",
                                "Model with \nrecalibrating \nVmaxG & dA4G")) +
  facet_wrap(vars(dose_uMadj), labeller = labeller(dose_uMadj = dose_names)) + 
  labs(shape = "Replicate") +
  xlab("Time (hours)") + ylab("Normalised glutathione (-)") + expand_limits(y=0) 

print(FigureS13)

if(SaveFigures == 1){
  ggsave("FigureS13.pdf", plot = FigureS13, path = "..//Figures", width = 20,
         height = 15, units = "cm", dpi = 300)
}

```

### Figure 4f: Glutathione model simulation for ketoconazole 
```{r}
GSHDoses_KET = unique(GSHData_KET$dose_uMadj)

GSHECs_KET = c(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (0.075/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (0.450/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (1.2/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (2.7/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (5.7/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"] + (12.2/20.3)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC1"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] + (4/62)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"] + (29/62)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"]),
        CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"] + (27/62)*(CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC3"] - CompoundParms_KET_M2$est_value[CompoundParms_KET_M2$X=="EC2"])
)

GSHParms_KET_M1 = PathwaysParms_KET_M2 %>% 
  rbind(filter(GSHParms_NIT_M2, !X %in% PathwaysParms_KET_M2$X))


GSHParms_KET_M2 = read.csv(file = "..//FittingResults//GSH_M2_20240722_142606_EB_KETModel_parameterEstimates_parmset6_cost_208.35.csv")
GSHParms_KET_M2 = GSHParms_KET_M2 %>%
  rbind(filter(GSHParms_KET_M1, !X %in% GSHParms_KET_M2$X))

GSHParms_KET_M3 = read.csv(file = "..//FittingResults//GSH_M3_20240722_150959_EB_KETModel_parameterEstimates_parmset36_cost_44.12.csv")
GSHParms_KET_M3 = GSHParms_KET_M3 %>%
  rbind(filter(GSHParms_KET_M1, !X %in% GSHParms_KET_M3$X))


GSHOutput_KET_M1 = run_model(GSHKET_M1, PathwaysTime, GSHDoses_KET,
                               GSHECs_KET, GSHInistate,
                               GSHParms_KET_M1$X,
                               GSHParms_KET_M1$est_value) 
GSHOutput_KET_M2 = run_model(GSHKET_M1, PathwaysTime, GSHDoses_KET,
                               GSHECs_KET, GSHInistate,
                               GSHParms_KET_M2$X,
                               GSHParms_KET_M2$est_value)
GSHOutput_KET_M3 = run_model(GSHKET_M1, PathwaysTime, GSHDoses_KET,
                               GSHECs_KET, GSHInistate,
                               GSHParms_KET_M3$X,
                               GSHParms_KET_M3$est_value)

Figure4f = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = filter(GSHData_KET, dose_uMadj %in% c(12.5, 100)), 
             aes(x = timeAfterExposure, y = data4modelReal, 
                 shape = as.factor(replID)), col = "gray", show_guide = FALSE) +
  geom_line(data = filter(GSHmean_KET, dose_uMadj %in% c(12.5, 100)), 
            aes(x = timeAfterExposure, y = mean,
                col = "Mean"),linewidth = 1.5) +
  #simulations
  geom_line(data = filter(GSHOutput_KET_M1, StateVar == "GSH" & 
                            dose_uMadj %in% c(12.5, 100)),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_KET_M2, StateVar == "GSH" &
                            dose_uMadj %in% c(12.5, 100)),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_KET_M3, StateVar == "GSH" &
                            dose_uMadj %in% c(12.5, 100)),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                     values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                     labels = c("Mean", "\nModel without \nrecalibration \n", 
                                "Model with \nrecalibrating \nVmaxG \n",
                                "Model with \nrecalibrating \nVmaxG & dA4G")) +
  facet_wrap(vars(dose_uMadj), labeller = labeller(dose_uMadj = dose_names)) +
  labs(shape = "Replicate") +
  xlab("Time (hours)") + ylab("Normalised glutathione (-)") + expand_limits(y=0) 

print(Figure4f)

GSHAIC_KET_M1 = compute_AIC(GSHData_KET, c("GSH"), 0, GSHKET_M1, GSHDoses_KET,
                            GSHECs_KET, GSHInistate, 
                            GSHParms_KET_M1$X, GSHParms_KET_M1$est_value)

GSHAIC_KET_M2 = compute_AIC(GSHData_KET, c("GSH"), 1, GSHKET_M1, GSHDoses_KET,
                            GSHECs_KET, GSHInistate,
                            GSHParms_KET_M2$X, GSHParms_KET_M2$est_value)

GSHAIC_KET_M3 = compute_AIC(GSHData_KET, c("GSH"), 2, GSHKET_M1, GSHDoses_KET,
                            GSHECs_KET, GSHInistate,
                            GSHParms_KET_M3$X, GSHParms_KET_M3$est_value)

if(SaveFigures == 1){
  ggsave("Figure4f.svg", plot = Figure4f, path = "..//Figures", width = 15,
         height = 6, units = "cm", dpi = 300)
}

```

### Supplementary Figure S14: all doses for glutathione model KET
```{r}
FigureS14 = ggplot(NULL) +
  theme_classic(base_size = 13) +
  # data mean & replicates
  geom_point(data = GSHData_KET, 
             aes(x = timeAfterExposure, y = data4modelReal, 
                 shape = as.factor(replID)), col = "gray") +
  geom_line(data = GSHmean_KET, aes(x = timeAfterExposure, y = mean, 
                                    col = "Mean"),linewidth = 1.5) +
  #simulations
  geom_line(data = filter(GSHOutput_KET_M1, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 1"), linewidth = 1.5) +
  geom_line(data = filter(GSHOutput_KET_M2, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 2"), linewidth = 1.5) +
    geom_line(data = filter(GSHOutput_KET_M3, StateVar == "GSH"),
            aes(x = time, y = value, col = "Model 3"), linewidth = 1.5) +
  scale_color_manual(name = "", breaks = c("Mean", "Model 1", "Model 2", "Model 3"),
                     values = c("Mean" = "black","Model 1" = "#31688EFF", 
                                "Model 2" = "#35B779FF", "Model 3" = "#FDE725FF"),
                     labels = c("Mean", "\nModel without \nrecalibration \n", 
                                "Model with \nrecalibrating \nVmaxG \n",
                                "Model with \nrecalibrating \nVmaxG & dA4G")) +
  facet_wrap(vars(dose_uMadj), labeller = labeller(dose_uMadj = dose_names)) +
  labs(shape = "Replicate") +
  xlab("Time (hours)") + ylab("Normalised glutathione (-)") + expand_limits(y=0) 

print(FigureS14)

if(SaveFigures == 1){
  ggsave("FigureS14.pdf", plot = FigureS14, path = "..//Figures", width = 20,
         height = 15, units = "cm", dpi = 300)
}

```
```{r}
#sessionInfo()
```
R version 4.3.3 (2024-02-29 ucrt)
Platform: x86_64-w64-mingw32/x64 (64-bit)
Running under: Windows 11 x64 (build 26100)

Matrix products: default


locale:
[1] LC_COLLATE=English_United Kingdom.utf8 
[2] LC_CTYPE=English_United Kingdom.utf8   
[3] LC_MONETARY=English_United Kingdom.utf8
[4] LC_NUMERIC=C                           
[5] LC_TIME=English_United Kingdom.utf8    

time zone: Europe/Amsterdam
tzcode source: internal

attached base packages:
[1] stats     graphics  grDevices utils     datasets 
[6] methods   base     

other attached packages:
 [1] svglite_2.1.3   deSolve_1.40    lubridate_1.9.3
 [4] forcats_1.0.0   stringr_1.5.1   dplyr_1.1.4    
 [7] purrr_1.0.2     readr_2.1.5     tidyr_1.3.1    
[10] tibble_3.2.1    ggplot2_3.5.1   tidyverse_2.0.0

loaded via a namespace (and not attached):
 [1] gtable_0.3.6      crayon_1.5.3      compiler_4.3.3   
 [4] tidyselect_1.2.1  textshaping_0.4.0 systemfonts_1.1.0
 [7] scales_1.3.0      yaml_2.3.10       fastmap_1.2.0    
[10] R6_2.5.1          labeling_0.4.3    generics_0.1.3   
[13] knitr_1.49        munsell_0.5.1     pillar_1.9.0     
[16] tzdb_0.4.0        rlang_1.1.4       utf8_1.2.4       
[19] stringi_1.8.4     xfun_0.49         viridisLite_0.4.2
[22] timechange_0.3.0  cli_3.6.3         withr_3.0.2      
[25] magrittr_2.0.3    digest_0.6.37     grid_4.3.3       
[28] rstudioapi_0.17.1 hms_1.1.3         lifecycle_1.0.4  
[31] vctrs_0.6.5       evaluate_1.0.1    glue_1.8.0       
[34] farver_2.1.2      ragg_1.3.3        fansi_1.0.6      
[37] colorspace_2.1-1  rmarkdown_2.29    tools_4.3.3      
[40] pkgconfig_2.0.3   htmltools_0.5.8.1
